### 2014-01-24 thesis/src/chapters/chapter-state-of-the-art.tex
Thesis: add cf-specific technological concepts and summary

@@

% do kminy - dopisac Bosha/DEA/Warden ?

>>>>

\subsubsection{Cloud Foundry-specific}
\begin{asparaenum}
\item[\textbf{Warden}] The main goal of \emph{Warden} is to manage isolated and resource-controller environments called containers. It is responsible for management of the whole lifecycle of an environment and provides API for actually performing any operation on a container. At first, \emph{Warden} used LXC technology under the hood, but now containers are an own product of \emph{Cloud Foundry} community.
\item[\textbf{Droplet Execution Agent}] \emph{DEA} manages \emph{Warden} containers, stages user's application and runs droplets -- wrappers around already deployed applications.
\item[\textbf{BOSH}] \emph{BOSH} is a tool chain for release, deployment and lifecycle management of distributed services. Its functionalities can be compared to those offered by \emph{Chef}.
\end{asparaenum}

@@

\subsection{Summary}
Owing to the variety of useful features, great support from community and significant IT enterprises such as IBM, VMware to name a few, \emph{Cloud Foundry} can be considered a mature product which can compete with current leaders in the fields, such as Amazon AWS.
Additionally, it is highly probable that acquiring the hosted solution by \emph{Pivotal} may be of a great benefit to the whole cloud community as the market will be more competitive.
